Predicting Which States are Most Interested in the term *China Virus* Based off Identity Politics, Demography and COVID-19 Statistics 

### 2020-05-05 Final-Draft.Rmd
final changes w alicia

### Model Structure
$$\begin{aligned}
Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 &\overset{ind}{\sim} N(\beta_0+ \beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4,\sigma^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
\sigma &\sim Exp(...)\\
\end{aligned}$$

@@

$$\begin{aligned}
Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b &\sim N(\theta_i +\beta_1X_1 + \beta_2X_2 + \beta_3X_3+ \beta_4X_4, \sigma_w^2)\\
\theta_i|\mu, \sigma_b &\overset{ind}{\sim}N (\mu, \sigma_b^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
\sigma_w,\sigma_b &\sim Exp(...)\\
\end{aligned}$$

@@

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 \sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_2 + \beta_3X_3 +\beta_4X_4, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0,\beta_1,\beta_2,\beta_3,\beta_4 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$
In this hierarchical model each state receives a specific slope and intercept. The first step is determined through determining the $\beta_{0} - \beta_{4}$ values which represent the intercept, slope, and our three demographic interactions that we bring in from model 3. The $\beta_{0}$ represents the intercept value for all states. From this value each state derives its individual $b_{0i}$ which represents that state’s individual intercept value. In the diagram below we see that the $b_{0i}$ values are normally distributed around the $\beta_{0}$ and are distributed by $\sigma_{0b}$. This same process occurs for determining state specific slopes however we use $\beta_{1}$ and $b_{1i}$.

@@

In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero we could argue that random slopes are not necessary, but the mean of  $\sigma_{1b}^2$ is around 2-2.5. Similar to our previous dens overlay checks our value of $\sigma_b^2$ is almost always above zero and its mean is around 75, which means that random intercepts are necessary.

@@

We believe that the decreases in mae and increases of the proporiton of values observed within 50% of the posterior predictive interval do not justify increasing the complexity. Which is why we argue that Model 3 is the best model because it acchieves similar results to model 4 without making it computationally expensive. But if we want a more precise model we would use Model 4.

@@

In this table each model's prediction of Florida on the final day of our target window compared with how the actual value in the set. We find that the predictions, especially with our more complex Models 3 & 4 are not particularly close, especially with Model 4 having an error of close to 6. However, we are aware that our MAEs have improved with the more sophisticated models.

@@

>>>>

### Model Structure
$$\begin{aligned}
Y_{i}|\beta_0, \beta_1, \beta_2,\beta_3,\beta_4 &\overset{ind}{\sim} N(\beta_0+ \beta_1X_{1i} + \beta_2X_{2i} + \beta_3X_{3i}+ \beta_4X_{4i},\sigma^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
\sigma &\sim Exp(...)\\
\end{aligned}$$

@@

$$\begin{aligned}
Y_{ij}|\theta,\mu,\beta_0, \beta_1, \beta_2,\beta_3,\beta_4,\sigma_w,\sigma_b &\sim N(\theta_i +\beta_1X_1 + \beta_2X_{2i} + \beta_3X_{3i}+ \beta_4X_{4i}, \sigma_w^2)\\
\theta_i|\mu, \sigma_b &\overset{ind}{\sim}N (\mu, \sigma_b^2)\\
\beta_0,\beta_1, \beta_2,\beta_3 &\sim N(...,...)\\
\sigma_w,\sigma_b &\sim Exp(...)\\
\end{aligned}$$

@@

$$
\begin{split}
Y_{ij} | b_0, b_1, \beta_0, \beta_1,\beta_2,\beta_3,\beta_4 ,\sigma_w, \sigma_{0b}, \sigma_{1b} & \sim N( b_{0i} + b_{1i} X_{ij}+ \beta_2X_{2i} + \beta_3X_{3i} +\beta_4X_{4i}, \; \sigma_w^2) \\
b_{0i} | \beta_0, \sigma_{0b} & \stackrel{ind}{\sim} N(\beta_0, \sigma_{0b}^2) \\
b_{1i} | \beta_1, \sigma_{1b} & \stackrel{ind}{\sim} N(\beta_1, \sigma_{1b}^2) \\
\beta_0,\beta_1,\beta_2,\beta_3,\beta_4 & \sim N(..., ...) \\
\sigma_w & \sim Exp(...) \\
\sigma_{0b} & \sim Exp(...) \\
\sigma_{1b} & \sim Exp(...) \\
\end{split}
$$
In this hierarchical model each state receives a specific slope and intercept. The first step is determined through determining the $\beta_{0} - \beta_{4}$ values which represent the intercept, slope, and our three demographic interactions that we bring in from model 3. The $\beta_{0}$ represents the intercept value for all states. From this value each state derives its individual $b_{0i}$ which represents that state’s individual intercept value. In the diagram below we see that the $b_{0i}$ values are normally distributed around the $\beta_{0}$ and are distributed by $\sigma_{0b}$. This same process occurs for determining state specific slopes however we use $\beta_{1}$ and $b_{1i}$.

@@

In the dens overlay we can see that our value for $\sigma_{1b}^2$ is close to zero but we could argue that random slopes are necessary, as the mean of  $\sigma_{1b}^2$ is around 2-2.5 and given that we are talking about slopes with not a very high range 2-2.5 is pretty good range for differing slopes. Similar to our previous dens overlay checks our value of $\sigma_b^2$ is almost always above zero and its mean is around 75, which means that random intercepts are necessary.

@@

We believe that the decreases in mae and increases of the proporiton of values observed within 50% of the posterior predictive interval do not justify increasing the complexity. Which is why we argue that Model 3 is the best model because it acchieves similar results to model 4 without making it computationally expensive. But if we want a more precise model we would use Model 4. But out mcmc_dens and our visualizations showed that there are different slopes across states and thus a more reasonable approach would be to use Model 4.

@@

In this table each model's prediction of Florida on the final day of our target window compared with how the actual value in the set. We find that the predictions, especially with our more complex Models 3 & 4 are not particularly close, especially with Model 4 having an error of close to 6. However, we are aware that our MAEs are smaller in Models 3 and 4.

@@

Truncated Normal Model** (0-100), really wide guesses.
